Entropy stable skew-symmetric discontinuous Galerkin formulations on non-conforming meshes

### 2018-10-19 docs/noncon/ext_decoupled_sbp.tex
updating talks + matlab

%\begin{frontmatter}
%\title{Skew-symmetric formulations for entropy stable discontinuous Galerkin methods on non-conforming meshes}
%
%\author[rice]{Jesse Chan\corref{cor1}}
%\ead{Jesse.Chan@caam.rice.edu}
%\address[rice]{Department of Computational and Applied Mathematics, Rice University, 6100 Main St, Houston, TX, 77005}
%
%\begin{abstract}
%Entropy stable high order methods for nonlinear conservation laws satisfy an inherent discrete entropy inequality.  
%\end{abstract}
%\end{frontmatter}

%\tableofcontents

@@

\section{Entropy stable Gauss-Legendre collocation methods}

@@

\section{Gauss-Legendre collocation on non-conforming meshes}

@@

\begin{figure}
\centering
\begingroup
\captionsetup{width=.25\linewidth}
\subfloat[Conforming faces]{\includegraphics[width=.25\textwidth]{figs/gauss1.png}}
\hspace{4em}
\subfloat[Non-conforming faces]{\includegraphics[width=.25\textwidth]{figs/gauss2.png}}
\endgroup
\caption{Examples of surface quadratures for conforming and non-conforming interfaces for Gauss collocation methods.  }
\label{fig:gqcon_noncon}
\end{figure}

@@

\note{Do we need 3 layers of surface nodes in 3D?  Interpolation to isotropic split-side nodes is a Kronecker product - does that reduce things down?  }

>>>>

%\begin{frontmatter}
%\title{Skew-symmetric formulations for entropy stable discontinuous Galerkin methods on non-conforming meshes}
%
%\author[rice]{Jesse Chan\corref{cor1}}
%\ead{Jesse.Chan@caam.rice.edu}
%\address[rice]{Department of Computational and Applied Mathematics, Rice University, 6100 Main St, Houston, TX, 77005}
%
%\begin{abstract}
%Entropy stable high order methods for nonlinear conservation laws satisfy an inherent discrete entropy inequality.  
%\end{abstract}
%\end{frontmatter}
%\tableofcontents

@@

\section{Entropy stable DG methods on tensor product elements}

@@

\section{Decoupled SBP operators for non-conforming meshes}

@@

%\begin{figure}
%\centering
%\begingroup
%\captionsetup{width=.25\linewidth}
%\subfloat[Conforming faces]{\includegraphics[width=.25\textwidth]{figs/gauss1.png}}
%\hspace{4em}
%\subfloat[Non-conforming faces]{\includegraphics[width=.25\textwidth]{figs/gauss2.png}}
%\endgroup
%\caption{Examples of surface quadratures for conforming and non-conforming interfaces for Gauss collocation methods.  }
%\label{fig:gqcon_noncon}
%\end{figure}

@@

\section{An efficient mortar-based implementation}

\subsection{Three-dimensional considerations}

\note{We need 3 layers of surface nodes in 3D.  Interpolation to isotropic split-side nodes can be done in a tensor-product fashion.  May not matter: interpolation on 2D faces to a refined set of 4 faces is $O(N^4)$ operations, so it doesn't change the overall cost of the code. }

\section{Numerical experiments}
